Improvement of crash forces in structures using optimization tools.

### 2016-08-05 paper.tex
Avances

\section{Acknowledgments}
The research leading to these results has received funding from the Spanish Government (Ministerio de Economía y Competitividad) under grant agreement DPI2013-41893-R. The authors fully acknowledge the support received.

>>>>

\section{Acknowledgments}
The research leading to these results has received funding from the Spanish Government (Ministerio de Econom\'ia y Competitividad) under grant agreement DPI2013-41893-R. The authors fully acknowledge the support received.
